---
title: "Macroeconomic Forcasting in R"
author: "charles MAWUSI"
date: "27/03/2022"
output: pdf_document
---

This applied study in Time Series follows the **EdX** Macroeconomic forecasting model. The course was originally taught in Eviews. I replicated the codes in R following the insight from Struya Packages used includes among others;

* Forecast 
* Tidyverse
* timetk
* lubricate

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      eval = TRUE, 
                      comment = "", 
                      warning = FALSE,
                      fig.width = 6, 
                      fig.height = 6,
                      fig.align='center',
                      dpi = 100,
                      bootstrap.thumbnail = FALSE)
options(width = 100)

```

## Data Processing 


```{r Libraries}

library(tidyverse)
library(ggplot2)
library(timetk)
library(dplyr)
library(forecast)

```

```{r load_data}
ARMA_et<-read.csv(file = file.choose(), header = T)
str(ARMA_et)
```

The mean of the data series in 3 decimal places is **`r round(mean(ARMA_et$et), 3)`** and the standard deviation is **`r round(sd(ARMA_et$et), 3)`**. Missing values in the date series is = **`r sum(is.null(ARMA_et))`**


```{r plot_data}

ARMA_et %>% plot.ts() %>% abline(h=mean(ARMA_et$et), col="red")

```

```{r simulate_AR(1)}

# simulating an AR(1) process: yt  = 3.0 + 0.55*yt-1 + et; y0 = 0

y_AR<-as.vector(1)
y_AR[1]<-0
n=500
for (i in 2:500){
  y_AR[i]<-3 + 0.55*(y_AR[i-1])+ARMA_et$et[i]
}
head(y_AR[5]) # fifth element 

```
```{r simulate_MA(1)}

# Generating an MA process  yt = -2.5 + et + 0.70 et-1 

y_MA<-as.vector(1)
y_MA[1]<-0
n=500
for (i in 2:500){
  y_MA[i]<--2.5 + ARMA_et$et[i]+0.7*ARMA_et$et[i-1]
}
y_MA[5]
 
```
```{r plot_MA_AR_series}

# Plot the ACF and PAC for the AR(1) and MA(1) Processes

par(mfrow =c(1, 3))
ts.plot(y_AR, main="Autoregressive-AR(1) Model")
acf(y_AR, "main=ACF(AR1)")
pacf(y_AR, main="PACF(AR1)")

par(mfrow =c(1, 3))
ts.plot(y_MA, main="Moving Average MA(1) Model")
acf(y_MA, main ="ACF MA(1)")
pacf(y_MA, main="PACF MA(1)")

```

