---
title: "Macroeconomic Forcasting in R"
author: "charles MAWUSI"
date: "27/03/2022"
output: pdf_document
---

This applied study in Time Series follows the **EdX** Macroeconomic forecasting model. The course was originally taught in Eviews. I replicated the codes in R following insight from Struya. Packages used includes among others;

* Forecast 
* Tidyverse
* timetk
* lubricate

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      eval = TRUE, 
                      comment = "", 
                      warning = FALSE,
                      fig.width = 6, 
                      fig.height = 6,
                      fig.align='center',
                      dpi = 100,
                      bootstrap.thumbnail = FALSE)
options(width = 100)

```

## Data Processing 


```{r Libraries}

library(tidyverse)
library(ggplot2)
library(timetk)
library(dplyr)
library(forecast)

```

```{r load_data}
ARMA_et<-read.csv(file = file.choose(), header = T)
str(ARMA_et)
```

The mean of the data series in 3 decimal places is **`r round(mean(ARMA_et$et), 3)`** and the standard deviation is **`r round(sd(ARMA_et$et), 3)`**. Missing values in the data series is = **`r sum(is.null(ARMA_et))`**


```{r plot_data}

ARMA_et %>% plot.ts() %>% abline(h=mean(ARMA_et$et), col="red")

```

## Simulating AR(1), MA(1), ARMA(1,1) Process 

```{r simulate_AR(1)}

# simulating an AR(1) process: yt  = 3.0 + 0.55*yt-1 + et; y0 = 0

y_AR<-as.vector(1)
y_AR[1]<-0
n=500
for (i in 2:500){
  y_AR[i]<-3 + 0.55*(y_AR[i-1])+ARMA_et$et[i]
}

```
```{r simulate_MA(1)}

# Generating an MA process  yt = -2.5 + et + 0.70 et-1 

y_MA<-as.vector(1)
y_MA[1]<-0
n=500
for (i in 2:500){
  y_MA[i]<--2.5 + ARMA_et$et[i]+0.7*ARMA_et$et[i-1]
}

```
The fifth observation of the MA(1) model is **`r round(y_MA[5], 3)`** and that of the AR(1) model is **`r round(y_AR[5], 3)`**


```{r plot_MA_AR_series}

# Plot the ACF and PAC for the AR(1) and MA(1) Processes

par(mfrow =c(1, 3))
ts.plot(y_AR, main="Autoregressive-AR(1) Model")
acf(y_AR, main="ACF AR(1)")
pacf(y_AR, main="PACF AR(1)")

par(mfrow =c(1, 3))
ts.plot(y_MA, main="Moving Average MA(1) Model")
acf(y_MA, main ="ACF MA(1)")
pacf(y_MA, main="PACF MA(1)")

```

```{r}
# Generating an ARMA process  yt = 0.5 + 0.5yt-1 +0.70et-1 + et 

ARMA<-as.vector(1)
ARMA[1]<-0
n=500
for (i in 2:n){
  ARMA[i]<-0.5+0.55*ARMA[i-1]+ARMA_et$et[i]+0.7*ARMA_et$et[i-1]
}

```
The fifth observation of the simulate ARMA is **`r round(ARMA[5], 3)`**


### Limit all Series ACF and PACF to A Maximum of 2 lags 

```{r  laggedACFPACF}

# Plot ACF and PACF for all the series with maximum lags 1 and 2 

par(mfrow =c(1, 3))
ts.plot(ARMA_et$et,  main="Innovation (et)")
acf(ARMA_et$et, lag.max = 2, main="ACF et ")
pacf(ARMA_et$et,lag.max = 2, main="PACF et")

par(mfrow =c(1, 3))
ts.plot(y_AR, main="Autoregressive-AR(1) Model")
acf(y_AR,lag.max = 2, main="ACF AR(1)")
pacf(y_AR,lag.max = 2,  main="PACF AR(2)")

par(mfrow =c(1, 3))
ts.plot(y_MA, main="Moving Average MA(1) Model")
acf(y_MA, lag.max = 2, main ="ACF MA(1)")
pacf(y_MA, lag.max = 2,  main="PACF MA(1)")

par(mfrow =c(1, 3))
ts.plot(ARMA, main="Moving Average ARMA(1, 1) ")
acf(y_MA,lag.max = 2,  main ="ACF ARMA(1)")
pacf(y_MA, lag.max = 2, main="PACF ARMA(1)")
```

```{r PACF Regression }
library(tidyr)
lm(y_AR~lag(y_AR, 1)+lag(y_AR, 2)) %>% summary()  # max of 2 lags 

```
### simulating and selecting appropriate models 

```{r}
library(forecast)
library(tidyverse)

Et<-rnorm(500, 0, 1)
yt<-as.vector(1)
yt[1]<-0
n=500
for (i in 2:n) {
  yt[i]<-0.5+0.7*yt[i-1]+Et[i]
}
yt %>% as.ts() %>% ts.plot()
par(mfrow=c(1, 2))
acf(yt)
pacf(yt)
Box.test(yt, lag = 10)
arimamodel<-auto.arima(yt)
summary(arimamodel)
plot(arimamodel$residuals)
acf(arimamodel$residuals)
Box.test(arimamodel$residuals)

```
The residual plots and tests from the **Arima model** selection procedure suggests an AR(1) process as a the best model that fit the yt time series data. 

### Aplication Real Data 

Here i use the new tidyquant package to extract data on renewable or grean energy stock index from NASDAQ

```{r NASDAQ}

library(tidyquant)

tk<-tq_exchange("NASDAQ") %>% tq_get("AAPL", from = "2007-01-01", to = "2016-12-31") %>% head()
tk


```

